\documentclass[12pt]{article}

\usepackage{fontspec}
\usepackage{geometry}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{url}
\usepackage{changepage}

\geometry{top=1in, bottom=1in, left=1.7in, right=1in, marginparsep=4pt, marginparwidth=1in}

\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancyplain}
\fancyhf{}
\cfoot{\thepage\ of \pageref{LastPage}}

\setlength{\parindent}{0pt}
%\setlength{\parskip}{12pt}

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{-16pt} % Slightly increase the distance of the margin years from the content
\reversemarginpar

\setromanfont{YaleNew}

\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text}

\begin{document}

\begin{center}
{\Large Taylor B. Arnold} \\
Curriculum Vitae
\end{center}

% AT\&T Labs Research       \\
% 33 Thomas Street          \\
% Floor 26                  \\
% New York, NY 10007

\vspace{6pt}

Yale University \\
Department of Statistics \\
24 Hillhouse Avenue \\
New Haven, CT 06511-6814 \\

Phone: 508 479-5975 \\
Fax: 203 432-0633 \\
Email: taylor.arnold{@}yale.edu \\
Website: \url{euler.stat.yale.edu/~tba3}

\vspace{24pt}

{\bf PROFESSIONAL APPOINTMENTS}
\vspace{12pt}

\years{2015 - Present}Yale University, Statistics, Lecturer  \\
\years{2014 - Present}AT\&T Labs Research, Senior Scientist

\vspace{24pt}

{\bf EDUCATION}
\vspace{12pt}

\years{2013} Ph.D. Statistics, Yale University \\
\hspace*{16pt} Thesis: “Inference with Ill-Conditioned Design Matrices” \\
\hspace*{16pt} Advisor: Sekhar Tatikonda \\
\hspace*{16pt} Co-Advisor: John Emerson \vspace{6pt}

\years{2009} M.A. Statistics, Yale University \vspace{6pt}

\years{2007} A.B. Mathematics, Bowdoin College \\
\hspace*{16pt} Thesis: “Convergence Properties of Simplex Optimization Algorithms”\\
\hspace*{16pt} Graduated {\it cum laude}

\vspace{24pt}

{\bf RESEARCH INTERESTS}
\vspace{12pt}

Statistical analysis of petabyte-scale data
\begin{adjustwidth}{16pt}{16pt}
develop new techniques, tools, and paradigms for analyzing very large
datasets (i.e., “big data”), with a particular focus on streaming,
spatiotemporal feeds
\end{adjustwidth} \vspace{6pt}

Penalized estimation
\begin{adjustwidth}{16pt}{16pt}
combine structurally penalized models with modern optimization theory to
enforce complex sparsity patterns in high-dimensional inference; applications
include image analysis, epidemiology, and spatial point processes
\end{adjustwidth} \vspace{6pt}

Applications to humanities data
\begin{adjustwidth}{16pt}{16pt}
collaborate with humanities scholars to visualize and extract meaning from
large text, image, and video corpora; engage in broad discourse of
Digital Humanities
\end{adjustwidth} \vspace{6pt}
\newpage

{\bf PUBLICATIONS}
\vspace{12pt}

{\bf Books}
\vspace{12pt}

% \years{2016}Arnold, Taylor. {\it Case Studies in Large-Scale Statistical Learning}. Under contract with Springer International Publishing. \vspace{0.25cm}

\years{2015}Arnold, Taylor and Lauren Tilton. {\it Humanities Data in R: Exploring Networks, Geospatial Data, Images, and Text}. New York: Springer International Publishing, 2015. doi: 10.1007/978-3-319-20702-5.

\vspace{12pt}
{\bf Refereed Journal Articles}
\vspace{12pt}

\years{2015}Arnold, Taylor, Lauren Tilton, Stacey Maples, and Laura Wexler. “Uncovering Latent Metadata in the FSA-OWI Photographic Archive”. {\it Digital Humanities Quarterly}. Accepted August 2015. \vspace{0.25cm}

\years{2014}Arnold, Taylor and Ryan Tibshirani. “Efficient Implementations of the Generalized Lasso Dual Path Algorithm.” {\it Journal of Computational and Graphical Statistics}. Accepted December 2014. doi: 10.1080/10618600.2015.1043010. \vspace{0.25cm}

\years{2013}Grippo, Tomas, John Liu, Nazlee Zebardast, Taylor Arnold, Grant Moore, and Robert Weinreb. “Twenty-Four–Hour Pattern of Intraocular Pressure in Untreated Patients with Ocular Hypertension.” {\it Investigative Ophthalmology \& Visual Science} 54.1 (2013): 512-517. doi: 10.1167/iovs.12-10709. \vspace{0.25cm}

\years{2011}Arnold, Taylor, and John Emerson. “Nonparametric goodness-of-fit tests for discrete null distributions.” {\it The R Journal} 3.2 (2011): 34-39. \vspace{0.25cm}

\years{2011}Emerson, John, and Taylor  Arnold. “Statistical sleuthing by leveraging human nature: A study of Olympic figure skating.” {\it The American Statistician} 65.3 (2011).\\doi: 10.1198/tast.2011.10165. \vspace{0.25cm}

\years{2010}Russett, Bruce, and Taylor Arnold. “Who talks, and who’s listening? Networks of international security studies.” {\it Security Dialogue} 41.6 (2010): 589-598.\\doi: 10.1177/09670106-10388205. \vspace{0.25cm}

\vspace{12pt}
{\bf Manuscripts in Submission}
\vspace{12pt}

\years{2015}Arnold, Taylor. “An Entropy Maximizing Geohash for Distributed Spatiotemporal Database Indexing". {\it ACM Transactions on Spatial Algorithms and Systems (TSAS)}. Submitted May 2015. arXiv:1506.05158 [cs.DB] \vspace{0.25cm}

\years{2015}Arnold, Taylor, Michael Kane, Simon Urbanek. “iotools: High-Performance I/O Tools for R.” {\it R Journal}. Submitted March 2015. \vspace{0.25cm}

\years{2015} Arnold, Taylor, Michael Kane, Simon Urbanek. “Computing Strategies for Fitting Regressions at Scale”. {\it Journal of Statistical Software}.  Submitted September 2015. \vspace{0.25cm}

\newpage

\vspace{8pt}
{\bf Conference Proceedings}
\vspace{12pt}

\years{2012} Arnold, Taylor, “Defining the Charter: Judicial Activism and the Supreme Court of Canada”. APSA 2012 Annual Meeting Paper. Available at SSRN: \url{http://ssrn.com/abstract=2109074} \vspace{0.25cm}

\years{2012} Arnold, Taylor. 2012. “User-Oriented High-Dimensional Linear Model Estimation”.
In JSM Proceedings, Statistical Computing Section. Alexandria, VA: American Statistical Association. 2429-2443. \vspace{0.25cm}

\vspace{8pt}
{\bf Manuscripts in Preparation}
\vspace{12pt}

Arnold, Taylor, Simon Byers, Simon Urbanek. “Sparse and Fast Spatial Density Estimation”. \vspace{0.25cm}

Arnold, Taylor, Lauren Tilton. “The NLP Pipeline and Deterministic Topic Constructions”. \vspace{0.25cm}

Arnold, Taylor. “An Affine Constrained Fused Lasso for Discrete Spatial Distributions”. \vspace{0.25cm}

Arnold, Taylor, Lauren Tilton. “Beyond a Bag of Words: New Feature Sets for Topic Models”. \vspace{0.25cm}

Arnold, Taylor, Michael Kane, Simon Urbanek. “Tools for the Datalake: Fast Queries over Large Deliminated Files”. \vspace{0.25cm}

\vspace{24pt}
{\bf TEACHING EXPERIENCE}
\vspace{12pt}

\years{2015-2016}{\bf Lecturer}, {\it Yale University}
\vspace{12pt}

\quad Data Mining and Machine Learning (Spring 2016)

\quad Linear Models (Fall 2015)

\vspace{12pt}
\years{2011}{\bf Visiting Lecturer}, {\it Connecticut College}
\vspace{12pt}

\quad Introduction to Statistics, two sections (Spring 2011)

\vspace{12pt}
\years{2010}{\bf Visiting Instructor}, {\it Yale University Summer College}
\vspace{12pt}

\quad Introduction to Statistics (Summer 2010)

\vspace{12pt}
\years{2010-2012}{\bf Teaching Assistant}, {\it Yale University}
\vspace{12pt}

\quad Advanced Data Analysis (Fall 2010, Spring 2012)

\quad Introductory Data Analysis (Spring 2011)

\quad Introductory Statistics (Fall 2011)

\quad Statistical Case Studies (Fall 2010)

\vspace{24pt}
{\bf INVITED TALKS}
\vspace{12pt}

\years{2016}Culture Analytics and User Experience Design, Instituate for Pure and Applied
Mathematics, UCLA, April 2016 \\
\years{2015}“Using in R in Humanities Research”, Institute for Liberal Arts Digital
Scholarship (ILiADS), Hamilton College, July 2015 \\
\years{2015}“High Performance Data I/O”, New England Statistics Symposium,
University of Connecticut, April 2015 \\
\years{2015}“Oh the Places We'll Go”, Department Seminar, Amherst College, February 2015 \\
\years{2013}“The Genlasso Package”, Connecticut R Users Group, New Haven, CT, February 2013\\
\years{2012}“Historical Data with Photogrammar”, University Library Colloquium, Columbia University, March 2012 \\
\years{2011}“The Best Guess: Comparing Bernoulli Estimators”, Department Seminar, Bowdoin College, November 2011

\vspace{24pt}
{\bf CONFERENCE ACTIVITY}
\vspace{12pt}

\years{2016}Joint Statistical Meetings, “What to do with messy data? Four case studies.” Chair and Organizer. Invited Session, 30 July - 4 August. \\
\years{2014}American Studies Association Annual Meeting, “Photogrammar: Organizing Visual Culture through Geography, Text Mining, and Statistical Analysis”. 7-12 July. \\
\years{2012}American Studies Association Annual Meeting, “Photogrammar in Puerto Rico: Reading the FSA's 1930s Visual Archive with Twenty-first-Century Visualization Tools”. 15-18 November. \\
\years{2012}Joint Statistical Meetings, “User Oriented High Dimensional Linear Model Estimation”, Contributed Talk, 28 July - 2 August. \\
\years{2012}Joint Statistical Meetings, “Statistical Sleuthing by Leveraging Human Nature”, Invited Poster, 28 July - 2 August. \\
\years{2012}useR! Meeting, “Package hdlm: Fitting High Dimensional Linear Models”, Contributed Talk, 12-15 June. \\
\years{2012}American Historical Association Annual Meeting, “From Archive to Interdisciplinary Tool: Transforming Our Image of the FSA-OWI Photograph Collection”, Contributed Talk, January 5-8.\\
\years{2011}American Studies Association Annual Meeting, “Digital Humanities Lightning Shorts”, Contributed Talk, 20-23 October. \\
\years{2011}useR! Meeting, “Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions”, Contributed Talk, 16-18 August.

\vspace{24pt}
{\bf AWARDS}
\vspace{12pt}

\years{2013}Yale Thesis Writing Prize \\
\years{2011-2015}NEH Digital Start-Up Grant, Photogrammar, Co-Director \\
\years{2008-2013}Yale Graduate Fellowship

\vspace{24pt}
{\bf ADVISING}
\vspace{12pt}

\years{2015-2016} David Marcano, Senior Thesis Advisor, Yale Statistics \\
\years{2015}Yutaro Yamada, Undergraduate Summer Intern, Yale Graphics Group

\vspace{24pt}
{\bf PROFESSIONAL SERVICE}
\vspace{12pt}

\years{2015-2016}American Statistical Association, Section Program Chair \\
\years{2015}Biometrika, Referee \\
\years{2014-2015}Journal of Statistical Software, Referee \\
\years{2013-2015}Neurology, Referee \\
\years{2012-2014}The R-Journal, Referee

\vspace{24pt}
{\bf UNIVERSITY SERVICE}
\vspace{12pt}

\years{2009-2013}Graduate Student Assembly, Statistics Representative \\
\years{2010-2011}Yale Tribunal, Member \\
\years{2010-2011}Yale Graduate School Executive Committee, Member

\vspace{24pt}
{\bf OTHER POSITIONS}
\vspace{12pt}

\years{2013-2014}Traveler's Insurance, Research and Development, Manager  \\
\years{2007-2008}IBM, Global Business Services, Consultant

\vspace{24pt}
{\bf PROFESSIONAL MEMBERSHIPS}
\vspace{12pt}

American Statistical Association (ASA) \\
Association for Computing Machinery (ACM) \\
American Mathematical Society (AMS)

\newpage

\vspace{24pt}
{\bf REFERENCES}
\vspace{12pt}

John Emerson \\
24 Hillhouse Avenue \\
New Haven, CT 06511 \\
john.emerson{@}yale.edu

\vspace{12pt}

Michael Kane \\
30 Thomas Street \\
New York, NY 10007 \\
kane{@}att.research.com

\vspace{12pt}

Sekhar Tatikonda \\
18 Hillhouse Avenue \\
New Haven, CT 06511-6607 \\
sekhar.tatikonda{@}yale.edu

\vspace{12pt}

Ryan Tibshirani \\
229B Baker Hall \\
Pittsburgh, PA 15213 \\
ryantibs{@}cmu.edu

\vspace{12pt}

Laura Wexler \\
100 Wall Street \\
New Haven, CT 06511-6607 \\
laura.wexler{@}yale.edu

\end{document}





